\documentclass[11pt, a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{parskip}
\usepackage{titlesec}
\usepackage{xcolor}
\definecolor{primary}{RGB}{124, 58, 237}
\titleformat{\section}{\Large\bfseries\color{primary}}{\thesection}{1em}{}
\usepackage{DejaVuSans}
\renewcommand{\familydefault}{\sfdefault}

\begin{document}

\begin{center}
    {\LARGE\bfseries Arkive Press Release}\\[0.5cm]
    {\large June 8, 2025}
\end{center}

\section{Arkive Launches Revolutionary Document Management Platform}
\textbf{San Francisco, CA} – Arkive, a new leader in document management, proudly announces the launch of its innovative platform on June 8, 2025. Designed to streamline organization and boost productivity, Arkive introduces a suite of powerful features wrapped in an elegant, user-friendly interface.

\subsection{Highlights}
\begin{itemize}
    \item \textbf{Launched Today}: Arkive is now available on web, iOS, and Android platforms.
    \item \textbf{Core Features}: Smart organization, intelligent reminders, secure storage, and cross-platform access.
    \item \textbf{Mission-Driven}: Committed to making document management effortless and delightful.
\end{itemize}

\subsection{Quote}
``We’re thrilled to introduce Arkive to the world. Our platform is built to simplify document management while keeping users ahead of their deadlines with intelligent reminders,'' said Jane Doe, CEO of Arkive.

\subsection{Availability}
Arkive is available for download at \texttt{https://arkive.app}. A free tier is offered with premium subscription options for advanced features.

\subsection{Contact}
For media inquiries, contact \texttt{press@arkive.app}.

\end{document}