\documentclass[11pt, a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{parskip}
\usepackage{titlesec}
\usepackage{xcolor}
\definecolor{primary}{RGB}{124, 58, 237}
\titleformat{\section}{\Large\bfseries\color{primary}}{\thesection}{1em}{}
\titleformat{\subsection}{\large\bfseries}{\thesubsection}{1em}{}
\usepackage{DejaVuSans}
\renewcommand{\familydefault}{\sfdefault}

\begin{document}

\begin{center}
    {\LARGE\bfseries Arkive Executive Bios}\\[0.5cm]
    {\large June 2025}
\end{center}

\section{Leadership Team}

\subsection{Jane Doe, CEO}
Jane Doe brings over 15 years of experience in technology leadership to Arkive. Previously, she served as a Senior Director at Google, where she led product development for cloud-based productivity tools. Jane holds an MBA from Stanford University and is passionate about building intuitive solutions for complex problems.

\subsection{John Smith, CTO}
John Smith is an expert in artificial intelligence and cloud infrastructure, with a decade of experience at Amazon Web Services. He spearheaded the development of Arkive’s intelligent reminder system. John holds a Ph.D. in Computer Science from MIT and is dedicated to advancing technology for user empowerment.

\subsection{Emily Chen, Head of Design}
Emily Chen is an award-winning designer with a focus on user experience. Her work has been recognized by the AIGA and Red Dot Awards. Before joining Arkive, she led design initiatives at Adobe. Emily holds a BFA from Parsons School of Design and drives Arkive’s elegant interface.

\section{Contact}
For media inquiries, contact \texttt{press@arkive.app}.

\end{document}