\documentclass[11pt, a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{parskip}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{xcolor}
\definecolor{primary}{RGB}{124, 58, 237}
\titleformat{\section}{\Large\bfseries\color{primary}}{\thesection}{1em}{}
\titleformat{\subsection}{\large\bfseries}{\thesubsection}{1em}{}
\usepackage{DejaVuSans}
\renewcommand{\familydefault}{\sfdefault}

\begin{document}

\begin{center}
    {\LARGE\bfseries Arkive Company Overview}\\[0.5cm]
    {\large June 2025}
\end{center}

\section{About Arkive}
Arkive is a revolutionary document management platform designed to simplify organization and enhance productivity. Launched in June 2025, Arkive combines an elegant, user-friendly interface with intelligent reminders to ensure users never miss a deadline. Our mission is to empower individuals and businesses to manage their documents with ease and confidence.

\section{Mission and Vision}
\subsection{Mission}
To provide a seamless, intuitive platform that transforms document management into an effortless and delightful experience.

\subsection{Vision}
To redefine how people interact with their documents, making organization accessible, intelligent, and beautiful for everyone.

\section{Key Features}
\begin{itemize}
    \item \textbf{Intuitive Dashboard}: A clean, centralized hub for all your documents.
    \item \textbf{Smart Organization}: Automatically categorize and tag documents for easy retrieval.
    \item \textbf{Intelligent Reminders}: AI-driven notifications to keep you on top of deadlines.
    \item \textbf{Secure Storage}: End-to-end encryption to protect your sensitive documents.
    \item \textbf{Cross-Platform Access}: Available on web, iOS, and Android.
\end{itemize}

\section{Team}
Arkive was founded by a team of innovators passionate about technology and design:
\begin{itemize}
    \item \textbf{Jane Doe}, CEO: Over 15 years in tech leadership, previously at Google.
    \item \textbf{John Smith}, CTO: Expert in AI and cloud infrastructure, formerly at Amazon.
    \item \textbf{Emily Chen}, Head of Design: Award-winning designer with a focus on user experience.
\end{itemize}

\section{Contact}
For more information, please contact our press team at \texttt{press@arkive.app}.

\end{document}